Applied Measure Theory for Probabilistic Modeling

### 2022-05-18 paper/paper.tex
edits

This begs the question: Why not just use the \href{https://en.wikipedia.org/wiki/Power_set}{\emph{power set}}, the ``set of all sets'', which is, after thinking about it, such a $\sigma$-algebra?

@@

\begin{itemize}
\item[$\bullet\!$]Borgstr\"om et al \cite{Borgstr_m_2013} describes the \verb|Fun| system in F\# in terms of \emph{measure transformer semantics}, but discusses only \emph{finite} measures.

>>>>

This raises the question: Why not just use the \href{https://en.wikipedia.org/wiki/Power_set}{\emph{power set}}, the ``set of all sets'', which is, after thinking about it, such a $\sigma$-algebra?

@@

\begin{itemize}
\item[$\bullet\!$]Borgstr\"om et al \cite{Borgstr_m_2013} describe the \verb|Fun| system in F\# in terms of \emph{measure transformer semantics}, but discusses only \emph{finite} measures.
